DOM Review Summary

### 2024-03-17 Analysis/ReviewSummary/ReviewSummary.qmd
Clean datacollection
create datacollection_clean object

species_taxaTable <-species_clean |>
  separate_rows(Taxa_Category, sep = ", ") |>
  mutate(Total = length(unique(ID_clean))) |>
  select(Taxa_Category, ID_clean, Total) |>
  distinct() |>
  summarise(Articles = n(), 
            Percentage = round(Articles/mean(Total), 2)*100,
            .by = Taxa_Category) |>
  arrange(-Articles) |>
  rename(Taxa = Taxa_Category)
```

@@

Only approximately half of articles modelled occupancy dynamics for a single taxa. Others fit multiple occupancy models: either multi-species models where 2+ taxa were modelled in concert, or many independent models for a suite of taxa. The largest number of species modelled in a single paper was **`{r} max(species_Number$Taxa_Number)`**.

@@

```{r DataCollection_clean}
#| echo: false

>>>>

species_taxaTable <- species_clean |>
  separate_rows(Taxa_Category, sep = ", ") |>
  mutate(Total = length(unique(ID_clean))) |>
  select(Taxa_Category, ID_clean, Total) |>
  distinct() |>
  summarise(Articles = n(), 
            Percentage = round(Articles/mean(Total), 2)*100,
            .by = Taxa_Category) |>
  arrange(-Articles) |>
  rename(Taxa = Taxa_Category)
```

@@

Only approximately half of articles modelled occupancy dynamics for a single taxa. Others fit multiple occupancy models: either multi-species models where 2+ taxa were modelled in concert, or many independent models fit for a suite of taxa. The largest number of species modelled in a single paper was **`{r} max(species_Number$Taxa_Number)`**.

@@

```{r DataCollection_clean}
#| echo: false
#| warning: false

dataCollection_clean <- review_DataCollection |>
  filter(Status == "Complete") |>
  mutate(Duration = as.numeric(Duration)) |>
  separate_wider_delim(cols = Primary_Occasions, 
                       delim = "-",
                       names = c("Primary_Min", "Primary_Max"),
                       too_few = "align_start") |>
  separate_wider_delim(cols = Secondary_Occasions, 
                       delim = "-",
                       names = c("Secondary_Min", "Secondary_Max"),
                       too_few = "align_start") |>
  separate_wider_delim(cols = Site_Number, 
                       delim = "-",
                       names = c("SiteNumber_Min", "SiteNumber_Max"),
                       too_few = "align_start") |>
  mutate(Primary_Max = if_else(is.na(Primary_Max),
                               Primary_Min, Primary_Max),
         Secondary_Max = if_else(is.na(Secondary_Max),
                                 Secondary_Min, Secondary_Max),
         SiteNumber_Max = if_else(is.na(SiteNumber_Max),
                                  SiteNumber_Min, SiteNumber_Max)) |>
  mutate(across(c(Primary_Min, Primary_Max, 
                  Secondary_Min, Secondary_Max,
                  SiteNumber_Min, SiteNumber_Max),
                as.numeric))
```
